### 2023-02-18 paper.tex
Added citavi

\section{Offline Concepts}
    \subsection{CAD/graphical based}
    \subsection{text based}
    \subsection{task based}
        \subsubsection{explicit}
        \subsubsection{implicit}
    \subsection{Simulation}

@@

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography} 
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

\section{Offline Concepts}

    \subsection{text based}

        uses problem solving programming languages 
        gives access to commands for movements with specific parameters for the specific movement

        programming enviroments for text based programming:
            \begin{itemize}
                \item KUKA 
                \item ABB RobotStudio
                \item Fanuc RobotStudio
                \item Staubli TX
                \item Adept
                \item Motoman
        (b1 p. 113)

    \subsection{task based}
        \subsubsection{explicit}
        \subsubsection{implicit}
    \subsection{CAD/graphical based}

    \subsection{Simulation}

@@

\begin{thebibliography}{00}
    \bibitem{b1} Wolfgang Weber, Heiko Koch, ''Industrieroboter Methoden der Steuerung und Regelung'' Carl Hanser Verlag München, 5. Auflage, 2022

\end{thebibliography} 
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.
